### 2019-04-02 1_introduction.tex
Apply Alex's and George's comments.

The challenge of parallel and distributed computation has lead to a
wide variety of proposals for programming models, languages, and
runtime systems. But while the features of these systems are widely
written about in the literature, comprehensive performance evaluations
of these systems remain difficult to find. Our
goal in this paper is to develop a meaningful and useful framework for
comparing the performance of parallel and distributed programming
systems.

@@

One approach to comparing the performance of different systems has
focused on the development of \emph{proxy-} or
\emph{mini-apps}. Because they distill the structure of a larger
application, mini-apps can provide insight
without the expense of developing a full-blown
application. However, despite the name, our experience is that
mini-apps still requite significant investment to develop, especially
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop the
mini-app in the first place. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Indeed, there are few such published studies that involve
more than a handful of systems.

There is another important issue: How does one predict how
the performance of a mini-app generalizes to a full
application, even one closely related? Part of the problem here is
that weak and strong scaling, which are by far the most commonly
reported metrics for performance of both mini- and full applications,
do not directly characterize the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead with sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from other costs
(such as increased communication, among other things) when
using progressively larger portions of a machine.

@@

A key insight of Task Bench is that many applications can be modeled
as a set of \emph{tasks}, or coarse-grain units of work, with
dependencies between tasks representing the communication required for
distributed execution. Task Bench consists of a configurable \emph{task graph} with tasks for
each point in an iteration space. Tasks are connected by dependencies
as determined by a \emph{dependence relation}. This design permits a
very concise description of a wide variety of patterns relevant to
scientific computing and large scale data analysis: trivial parallelism, halo exchanges (such as
seen in structured and unstructured mesh codes), sweeps (such as used
in the discrete ordinates method of radiation simulation), FFTs, trees
(for divide and conquer algorithms), and so on. The tasks at each
point in the task graph can be configured to execute kernels with a
variety of computational properties, including compute- and
memory-bound operations of varying durations. The dependencies between
tasks can be configured to carry payloads of varying size, permitting
the design of communication-bound cases. Finally, multiple
(potentially heterogeneous) task graphs can be executed concurrently
to introduce task parallelism into the workload. Together, these
design elements permit the exploration of a large space of application
behaviors.

To address the second issue and isolate the contribution of the programming model's runtime system
to application performance, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively,
METG(50\%) is the smallest application task granularity which can be
executed while maintaining at least 50\% computational efficiency,
meaning that the application achieves at least 50\% of peak
performance on a given machine. METG captures the essence of what is important in a weak
or strong scaling study, the behavior at the limit of scalability. For
weak scaling, METG(50\%) corresponds directly to the smallest problem
size that can be weak scaled with 50\% efficiency. For strong scaling,
METG(50\%) can be used to compute the scale at which performance can
be expected to dip below 50\% efficiency.

A lower METG does not necessarily mean that performance will be
better. For example, two systems with METG(50\%) of 100~us and 1~ms,
respectively, running an application with an average task granularity
of 10~ms, are both likely to perform well. Only when the task
granularity approaches (or drops below) METG(50\%) is performance
likely to diverge. Thus METG helps to identify the regime in which a
given system is likely to perform well.

@@

There is another, deeper issue with TPS. TPS may be measured with
empty tasks~\cite{LegionTracing18} or with tasks of some
duration~\cite{Canary16, Armstrong14}. If empty tasks are used, the
resulting upper bound on task scheduling throughput fails to represent
any realistic application, as no
useful work is being performed. If non-empty tasks are used, \emph{but
  the efficiency of the overall application is not reported}, then TPS
is not a measurement of runtime-limited performance. Large tasks may
be used to hide any amount of runtime overhead,
while tasks that are too small may result in a drop in total
application throughput even as TPS increases. Only by constraining
efficiency, as in METG, can we measure runtime-limited application
throughput while performing useful application work.

>>>>

The challenge of parallel and distributed computation has led to a
wide variety of proposals for programming models, languages, and
runtime systems. But while these systems are well-represented in the literature, comprehensive and comparative performance evaluations
remain difficult to find. Our
goal in this paper is to develop a meaningful and useful framework for
comparing the performance of parallel and distributed programming
systems.

@@

One approach to comparing the performance of different systems is through \emph{proxy-} or
\emph{mini-apps}. Because they distill the structure of a larger
application, mini-apps can provide insight
without the expense of developing a production code. However, despite the name, our experience is that
mini-apps still requite significant investment to develop
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop the
mini-app in the first place. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Indeed, there are few published studies
that involve more than a handful of systems~\cite{LULESH13}.

There is a second important issue: How does one predict how
the performance of a mini-app generalizes to a full
application, even one closely related? Part of the problem is
that \emph{weak} and \emph{strong} scaling, which are by far the most commonly
reported performance metrics,
do not directly characterize the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead with sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from other costs
(such as increased communication, among many other things) when
using progressively larger portions of a machine.

@@

A key insight of Task Bench is that many applications can be modeled
as a set of \emph{tasks}, or coarse-grain units of work, with
dependencies between tasks representing the communication required for
distributed execution. Task Bench consists of a configurable \emph{task graph} with tasks for
each point in an iteration space. Tasks are connected by dependencies
as determined by a \emph{dependence relation}. This design permits a
very concise description of a wide variety of patterns relevant to
scientific computing and large scale data analysis: trivial parallelism, halo exchanges (such as
seen in structured and unstructured mesh codes), sweeps (such as used
in the discrete ordinates method of radiation simulation), FFTs, trees
(for divide and conquer algorithms), and so on. The tasks at each
point in the task graph can be configured to execute kernels with a
variety of computational properties, including compute- and
memory-bound operations of varying durations. The dependencies between
tasks can be configured to carry communication payloads of varying size, permitting
the design of communication-bound cases. Finally, multiple
(potentially heterogeneous) task graphs can be executed concurrently
to introduce task parallelism into the workload. Together, these
design elements permit the exploration of a large space of application
behaviors.

To address the second issue and isolate the contribution of the programming model's runtime system
to application performance, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively,
METG(50\%) is the smallest application task granularity which can be
executed while maintaining at least 50\% efficiency,
meaning that the application achieves at least 50\% of peak
performance (e.g., FLOPS or memory bandwidth) 
on a given machine. METG captures the essence of what is important in a weak
or strong scaling study, the behavior at the limit of scalability. For
weak scaling, METG(50\%) corresponds directly to the smallest problem
size that can be weak scaled with 50\% efficiency. For strong scaling,
METG(50\%) can be used to compute the scale at which performance can
be expected to dip below 50\% efficiency.

A lower METG does not necessarily mean that performance for a particular workload will be
better. For example, two systems with METG(50\%) of 100~us and 1~ms,
respectively, running an application with an average task granularity
of 10~ms, are both very likely to perform well. Only when the task
granularity approaches (or drops below) METG(50\%) will performance
likely diverge. Thus METG helps to identify the regime in which a
given system can deliver good performance.

@@

There is another, deeper issue with TPS. TPS may be measured with
empty tasks~\cite{LegionTracing18} or with tasks of some
duration~\cite{Canary16, Armstrong14}. If empty tasks are used, the
resulting upper bound on task scheduling throughput fails to represent
any realistic application, as no
useful work is being performed. If non-empty tasks are used, \emph{but
  the efficiency of the overall application is not reported}, then TPS
is not a measurement of runtime-limited performance. Large tasks may
be used to hide any amount of runtime overhead,
while tasks that are too small may result in a drop in total
application throughput even as TPS increases. Only by constraining
efficiency, as in METG, can we meaningfully measure how runtime
overhead impacts the ability perform useful application work.

### 2019-04-02 2_metg.tex
Apply Alex's and George's comments.

\section{METG (50\%)}
\label{sec:metg}

@@

The \emph{minimum effective task granularity}, METG(50\%), for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency exceeding 50\%. For example, in
a compute-bound application efficiency might be measured as the
percentage of the available FLOPS achieved. On a machine with a peak
capability of 1.26 TFLOPS per node, METG(50\%) would correspond to
the smallest task granularity achieved while maintaining at least 0.63
TFLOPS. Relative parallel efficiency (vs a sufficiently large problem
size) can also be used in cases where the application isn't easily
characterized by peak resource usage.

@@

In Figure~\ref{fig:efficiency-mpi}, we see that
efficiency starts near 100\%, and that initially task granularity
drops quickly with minimal change in efficiency. However as task
granularity shrinks further, efficiency begins to drop as well, leading
eventually to a plateau in task granularity. Intuitively, this plateau
represents the fundamental baseline overhead of the system, the point
below which the system simply cannot execute tasks efficiently.

METG(50\%) is the intersection of this curve with a vertical line through
Figure~\ref{fig:efficiency-mpi} at 50\% efficiency. In the figures, the red, dashed line shows the 50\% efficiency
level. At 50\% efficiency, MPI achieves an average task granularity of
4.6 us, thus the METG(50\%) of MPI is 4.6 us for this configuration of
Task Bench. We use 50\% because it is a reasonable level of
efficiency in practice. Lower values would likely not be reasonable,
because operators of computing facilities prefer higher levels of
utilization. Values above 90\% can misrepresent the performance of
some systems (see
Section~\ref{subsec:peak-performance-and-efficiency}).

METG is an appealing metric in part because it has a well-defined
relationship with quantities of interest to application developers,
namely weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the behavior of the MPI Task Bench stencil's weak and strong
scaling, respectively, at a variety of problem sizes. Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to appear at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes dominated by overhead. The shape of the curve at the bottom is the same
for both weak and strong scaling; this is the shape of
the METG curve.

@@

METG therefore has a direct relationship with the smallest problem
size that can be weak scaled to a given node count with a given level
of efficiency. With any smaller problem size, 
the runtime overhead begins to dominate useful
computation. Similarly, METG corresponds to the point at which strong
scaling can be expected to stop; as strong scaling runs start with a
larger problem size and progressively shrink it until overheads begin
to dwarf the gains due to continued scaling. In
Figures~\ref{fig:weak-scaling-mpi} and \ref{fig:strong-scaling-mpi},
the dashed, bright red line show the value of METG(50\%) at each node
count.

>>>>

\section{METG}
\label{sec:metg}

@@

The \emph{minimum effective task granularity}, METG(50\%), for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency exceeding 50\%. For example, in
a compute-bound application efficiency might be measured as the
percentage of the available FLOPS achieved. On a machine with a peak
capability of 1.26 TFLOPS per node, METG(50\%) would correspond to
the smallest task granularity achieved while maintaining at least 0.63
TFLOPS. Absolute (rather than relative) efficiency is preferred
because it makes it easier to conduct fair comparisons with
programming systems that reserve one or more cores for internal use.

@@

In Figure~\ref{fig:efficiency-mpi}, we see that
efficiency starts near 100\%, and that initially task granularity
drops quickly with minimal change in efficiency. However as task
granularity shrinks further, efficiency begins to drop more rapidly, leading
eventually to asymptote. Intuitively, this asymptote
represents the fundamental baseline overhead of the system, the point
below which the system simply cannot execute tasks efficiently.

% FIXME: keep this up-to-date with the graphs

METG(50\%) is the intersection of this curve with 50\% efficiency, as
shown by the red lines in Figure~\ref{fig:flops-mpi} and
\ref{fig:efficiency-mpi}. At 50\% efficiency, MPI achieves an average
task granularity of
4.6 us, thus the METG(50\%) of MPI is 4.6 us for this configuration of
Task Bench. We use 50\% because that is generally an acceptable level
of efficiency in practice, and values above 90\% can misrepresent the
performance of some systems (see
Section~\ref{subsec:peak-performance-and-efficiency}).

METG has a well-defined
relationship with quantities of interest to application developers,
namely weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the behavior of the MPI Task Bench stencil's weak and strong
scaling, respectively, at a variety of problem sizes. In these
figures, the vertical axis is shown as wall time to emphasize the
relationship to time-to-solution, but it could equivalently be shown
as task granularity (as the number of tasks per execution is
fixed). Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to appear at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes dominated by overhead. The shape of the curve at the bottom is the same
for both weak and strong scaling; this is
the METG curve.

@@

METG therefore has a direct relationship with the smallest problem
size that can be weak scaled to a given node count with a given level
of efficiency. With smaller problem sizes runtime overhead increasingly dominates useful
computation. Similarly, METG corresponds to the point at which strong
scaling can be expected to stop; as strong scaling runs start with a
larger problem size and progressively shrink it until overheads begin
to dwarf the gains due to continued scaling. In
Figures~\ref{fig:weak-scaling-mpi} and \ref{fig:strong-scaling-mpi},
the dashed, bright red line show the value of METG(50\%) at each node
count.

### 2019-04-02 3_task_bench.tex
Apply Alex's and George's comments.

For simplicity, but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, each column $i$ corresponds to all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column of the task graph will be
assigned to execute on a different processor core.

@@

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The core aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the Task Bench core library manages the
parsing of input parameters and the display of output results,
ensuring that all implementations behave in a uniform manner, and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 13 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being typical.

The Task Bench core library is fully
validating. Because the task graph configuration is explicitly
represented (though unmaterialized) in Task Bench, this representation
can be queried to determine exactly what dependencies a task should
expect. The output of every task in Task Bench is unique,
and all inputs are verified. An assertion is thrown if validation
fails. This level of self-checking ensures that every execution of Task Bench, if it
completes successfully, is correct. An evaluation of the impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

>>>>

For simplicity, but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, column $i$ represents all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column of the task graph will be
assigned to execute on a different processor core.

@@

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The central aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the Task Bench core library manages the
parsing of input parameters and the display of output results,
ensuring that all implementations behave in a uniform manner and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 13 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being typical.

The Task Bench core library is fully
validating. Because the task graph configuration is explicitly
represented (though unmaterialized) in Task Bench, this representation
can be queried to determine exactly what dependencies a task should
expect. The output of every task in Task Bench is unique,
and all inputs are verified. An assertion is thrown if validation
fails. This level of self-checking ensures that every execution of Task Bench, if it
completes successfully, is correct. An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

### 2019-04-02 4_implementation.tex
Apply Alex's and George's comments.

There are also aspects of some systems that we do not consider in our
evaluation. For example, a number of systems provide some level of
support for heterogeneous processors such as GPUs, but the support
varies so widely (if it exists at all) that it is challenging to come
up with a representative benchmark that allows these features to be
compared in an apples-to-apples manner.

@@

Chapel~\cite{Chapel15} is a programming language
that follows a \emph{multi-res\-o\-lu\-tion} approach to parallel
programming, with support for parallelism at a variety of
levels. Chapel's core features are a partitioned global address space
(PGAS), data distributions, tasks,
synchronization primitives, and array promotion. For Task Bench, we decided to target a low-level implementation in
Chapel, using explicit task instantiation (via
\lstinline[language=Chapel]{coforall}), bulk access to distributed
arrays for efficient data movement, and atomic integers for
synchronization.

@@

Charm++~\cite{Charmpp93} is an explicitly parallel programming system
based on the actor model. Actors, or
\emph{chares}, are objects that live in their own address space;
chares communicate data and synchronize via messages, and can be moved
to balance load. Our Task Bench implementation uses a chare
array for the task graph, with one chare for each column of the task graph. Messages are
used to implement dependencies, and a task is executed as soon as its
dependencies are all available. Collectives are used to synchronize the
completion of the task graph execution.

@@

Our MPI~\cite{MPI} implementation of Task Bench represents the common
case of bulk synchronous programs with distinct computation and
communication phases. We experimented with a variety of implementation
strategies and found the best performing to be using
\lstinline[language=C++]{MPI_Isend} and
\lstinline[language=C++]{MPI_Irecv} to implement the communication
phase, posting receives before sends. Each task dependency maps to one
send/receive pair in MPI.

@@

In our evaluation, we test with both GNU GOMP and Intel KMP
implementations of OpenMP. We found KMP to provide better performance
and thus report KMP numbers in our evaluation.

@@

In the DTD model, tasks are enumerated in program order (by
executing the program), and dependencies between tasks are
identified automatically based on the input and output data of tasks. 
A task depends on another task if it reads data written by the other task,
and the data is copied automatically if the two tasks are executed on
different nodes. While the basic DTD model is implicitly parallel
because the system is responsible for the discovery of parallelism, to
achieve horizontal scalability, the program is executed in a
SPMD fashion on all nodes, and the user is responsible for eliding
tasks that are not directly connected to those that are to be executed
on the current node.

@@

Realm~\cite{Realm14} is an explicitly-parallel task-based programming
model used internally by Legion~\cite{Legion12} and
Regent~\cite{Regent15}. Thus the Realm implementation of Task Bench can be
seen as a limit study of what can be achieved with Legion or Regent.

@@

Realm also supports a subgraph API where sets of tasks and copies are
issued together. This mode permits additional optimizations to be
performed. We have implemented Task Bench in both individual and
subgraph styles, but report numbers for the subgraph version as it
provides better performance.

@@

The core abstractions in Spark are functional operators such as map,
reduce, filter, join, etc. Functions in Spark operate on
\emph{resilient
  distributed datasets} (RDDs), which are globally-visible,
dynamically single-assignment data structures that are cached in memory
and written to disk for durability. One of Spark's primary
optimizations therefore is the caching of RDDs to avoid unnecessary
disk traffic.

Though Spark has tasks internally, these are not exposed to the user,
so one of the challenges in developing a Task Bench implementation is
mapping the task graph to a set of operators which will result in the
desired performance behavior. We use a combination of
\lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} operations to generate task
dependencies, and then \lstinline[language=Scala]{mapPartitions} to execute a
series of tasks. We use an explicit hash partitioner to ensure that
Spark does not attempt to group multiple Task Bench tasks into a
single Spark task.

We performed an extensive set of experiments to verify that no
extraneous factors interfered with our Spark measurements. We
completely disabled logging, ensured that no RDDs are actually written
to disk, confirmed that there is no measurable overhead due to JNI
calls from Java to C, and cross-checked our results with known cases
that hit optimal task throughput in Spark, among other things.

@@

Swift/T~\cite{Wozniak13} is a parallel scripting language intended
primarily for the composition of workflows in high-performance
scientific computing. Tasks in Swift/T can be written in any
programming language, and may even be themselves parallel. Swift/T
programs follow dataflow semantics, where every statement may
potentially execute in parallel as soon as its dependencies are
satisfied; statements only execute sequentially when explicitly
requested. The Swift/T compiler performs a number of optimizations to
improve performance of highly parallel programs~\cite{Armstrong14}.

@@

TensorFlow~\cite{TensorFlow15} is a programming system intended for
the executing deep learning workloads, widely used in industrial data
center applications. Although TensorFlow's high-level API exposes
concepts specific to machine learning, internally TensorFlow is
implemented as a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs are written by creating nodes in the
task graph, and then connecting these nodes with edges to implement
the desired dataflow. Task graphs are composed in a high-level
language such as Python, but then serialized and run by an
execution engine written in C++.

>>>>

There are also aspects of some systems that we do not consider in our
evaluation. For example, a number of systems provide some level of
support for heterogeneous processors such as GPUs, but the support
varies so widely (if it exists at all) that it seems difficult to
compare systems with direct GPU support to those wihtout in an
apples-to-apples manner.

@@

Chapel~\cite{Chapel15} is a parallel programming language
with a \emph{multi-res\-o\-lu\-tion} approach, supporting parallelism at a variety of
levels. Chapel's core features are a partitioned global address space
(PGAS), data distributions, tasks,
synchronization primitives, and array promotion. For Task Bench, we target a low level of
Chapel, using explicit task instantiation (via
\lstinline[language=Chapel]{coforall}), bulk access to distributed
arrays for efficient data movement, and atomic integers for
synchronization.

@@

Charm++~\cite{Charmpp93} is an explicitly parallel actor-based programming system. Actors, or
\emph{chares}, are objects in their own address space.
Chares communicate data and synchronize via messages and can be moved
to balance load. Our Task Bench implementation uses a chare
array for the task graph, with one chare for each column. Messages implement dependencies; a task executes as soon as its
dependencies are all available. Collectives synchronize the
completion of the task graph execution.

@@

% FIXME: bulk synchronous or point-to-point

Our MPI~\cite{MPI} implementation of Task Bench represents the common
case of point-to-point communication with distinct computation and
communication phases. We experimented with a variety of implementation
strategies and found the best performing to be using
\lstinline[language=C++]{MPI_Isend} and
\lstinline[language=C++]{MPI_Irecv} to implement the communication
phase, posting receives before sends. Each task dependency maps to one
send/receive pair in MPI.

@@

In our evaluation, we test with both GNU GOMP and Intel KMP
implementations of OpenMP. We found KMP to provide better performance
and report KMP numbers in our evaluation.

@@

In the DTD model, tasks are enumerated in program order (by
executing the program), and dependencies between tasks are
identified automatically based on the input and output data of tasks. 
A task depends on another task if it reads data written by the other task,
and the data is copied automatically if the two tasks are executed on
different nodes. To
improve horizontal scalability, the program is executed in
SPMD fashion on all nodes, and the user is responsible for eliding
tasks that are not directly connected to those that are to be executed
on the current node.

@@

Realm~\cite{Realm14} is an explicitly-parallel task-based programming
model used internally by Legion~\cite{Legion12} and
Regent~\cite{Regent15}. A Realm implementation of Task Bench is a limit study of what can be achieved with Legion or Regent.

@@

Realm also supports a \emph{subgraph} API that enables additional
optimizations. We report numbers for the subgraph version of Task
Bench as it provides better performance.

@@

The core abstractions in Spark are functional operators such as map,
reduce, filter, join, etc. Functions in Spark operate on
\emph{resilient
  distributed datasets} (RDDs), which are globally-visible,
dynamically single-assignment data structures. One of Spark's primary
optimizations is the caching of RDDs to avoid unnecessary
disk traffic.

Though Spark has tasks internally, these are not exposed to the user,
so one of the challenges in developing a Task Bench implementation is
mapping the task graph to a set of operators that result in the
desired performance behavior. We use a combination of
\lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} operations to generate task
dependencies, and then \lstinline[language=Scala]{mapPartitions} to execute a
series of tasks. We use an explicit hash partitioner to ensure that
Spark does not attempt to group multiple Task Bench tasks into a
single Spark task, as the tasks in Task Bench already represent coarse-grained units of work.

We performed extensive experiments to verify that no
extraneous factors interfered with our Spark measurements. We
completely disabled logging, ensured no RDDs are written
to disk, confirmed there is no measurable overhead due to JNI
calls from Java to C, and cross-checked results with known cases
that hit optimal task throughput in Spark, among other things.

@@

Swift/T~\cite{Wozniak13} is a parallel scripting language intended
primarily for the composition of HPC workflows. Tasks in Swift/T can be written in any
programming language, and may even be themselves parallel. Swift/T
programs follow dataflow semantics, where every statement may
potentially execute in parallel as soon as its dependencies are
satisfied; statements only execute sequentially when explicitly
requested. The Swift/T compiler performs a number of optimizations to
improve performance of highly parallel programs~\cite{Armstrong14}.

@@

TensorFlow~\cite{TensorFlow15} is a programming system designed for
deep learning workloads. Although TensorFlow's API exposes
machine learning concepts, internally TensorFlow is a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs are written by creating nodes in the
task graph, and then connecting these nodes with edges to implement
the desired dataflow. Task graphs are composed in a high-level
language such as Python, but then serialized and run by an
execution engine written in C++.
